---
title: "Statistical Method HW1"
author: "徐仁瓏 RE6121011"
date: "2023-09-12"
output: html_document
---

```{r}
data("iris")
dat = iris
head(dat)
```


## 1. What are the types of variables?

`Sepal.Length` : cardinal

`Sepal.Width`  : cardinal

`Petal.Length` : cardinal

`Petal.Width`  : cardinal

`Species`      :  nominal


## 2. For each variables, give the histogram/barplot and boxplot.


> Sepal.Length


```{r, echo=FALSE}
par(mfrow=c(1,2))
hist(dat$Sepal.Length, xlab='Sepal.Length', main='Histogram')
boxplot(dat$Sepal.Length, xlab='Sepal.Length', main='Boxplot')
```


> Sepal.Width

```{r, echo=FALSE}
par(mfrow=c(1,2))
hist(dat$Sepal.Width, xlab='Sepal.Width', main='Histogram')
boxplot(dat$Sepal.Width, xlab='Sepal.Width', main='Boxplot')
```

> Petal.Length

```{r, echo=FALSE}
par(mfrow=c(1,2))
hist(dat$Petal.Length, xlab='Petal.Length', main='Histogram')
boxplot(dat$Petal.Length, xlab='Petal.Length', main='Boxplot')
```

> Petal.Width

```{r, echo=FALSE}
par(mfrow=c(1,2))
hist(dat$Petal.Width, xlab='Petal.Width', main='Histogram')
boxplot(dat$Petal.Width, xlab='Petal.Width', main='Boxplot')
```

> Species

```{r, echo=FALSE}
barplot(table(dat$Species) ,main='Bar Chart') 
```





## 3. Use a table to summarize variables with the descriptive statistics including mean, median, variance, standard deviation, range, IQR, skewness, and kurtosis.

```{r , echo=FALSE}
library(moments)

df = data.frame(
  Variables = c('Sepal.Length', 'Sepal.Width', 'Petal.Length', 'Petal.Width') , 
  Mean = c(mean(dat$Sepal.Length), mean(dat$Sepal.Width), mean(dat$Petal.Length), mean(dat$Petal.Width)) , 
  Median = c(median(dat$Sepal.Length), median(dat$Sepal.Width), median(dat$Petal.Length), median(dat$Petal.Width)) , 
  Variance = c(var(dat$Sepal.Length), var(dat$Sepal.Width), var(dat$Petal.Length), var(dat$Petal.Width)) , 
  SD = c(sd(dat$Sepal.Length), sd(dat$Sepal.Width), sd(dat$Petal.Length), sd(dat$Petal.Width)) , 
  Range = c(max(dat$Sepal.Length)-min(dat$Sepal.Length), max(dat$Sepal.Width)-min(dat$Sepal.Width), max(dat$Petal.Length)-min(dat$Petal.Length), max(dat$Petal.Width)- min(dat$Petal.Width)) , 
  IQR = c(as.numeric(quantile(dat$Sepal.Length,3/4)-quantile(dat$Sepal.Length,1/4)),
          as.numeric(quantile(dat$Sepal.Width,3/4)-quantile(dat$Sepal.Width,1/4)),
          as.numeric(quantile(dat$Petal.Length,3/4)-quantile(dat$Petal.Length,1/4)),
          as.numeric(quantile(dat$Petal.Width,3/4)-quantile(dat$Petal.Width,1/4))) ,
  Skewness = c(skewness(dat$Sepal.Length), skewness(dat$Sepal.Width), skewness(dat$Petal.Length), skewness(dat$Petal.Width)) , 
  Kurtosis = c(kurtosis(dat$Sepal.Length), kurtosis(dat$Sepal.Width), kurtosis(dat$Petal.Length), kurtosis(dat$Petal.Width))
)
```
```{r results = 'asis' ,echo=FALSE}
knitr::kable(df, caption = 'Table with IRIS data')
```

## 4. Are all cardinal variables symmetric?

> According to the histogram & boxplot above, we can easily see that `Petal.Length` & `Petal.Width` are NOT symmetric. 

> However, the histogram of `Sepal.Length` & `Sepal.Width` seem to look like Normal distribution, but when we take a look at its boxplot very carefully, we can see that `Sepal.Length` & `Sepal.Width` are NOT symmetric either.

## 5. Is there any outlier?

> According to the boxplot above, we can see that there are NO outliers in the variables `Sepal.Length`, `Petal.Length`, `Petal.Width`. 

> However, there are 4 outliers in the variable `Sepal.Width`.


