---
title: "Statistical Method HW5"
author: "RE6121011 徐仁瓏"
date: "2023-10-31"
output: html_document
---


## Given the sepal width of ”iris” data, use the following steps to show if the mean of sepal width is 3. Assume the sepal widths are random samples from a normal distribution

```{r}
data(iris)
x = iris$Sepal.Width
```

## (a) Use the maximum likelihood estimation method to estimate the model parameters of the normal distribution. 

```{r}
set.seed(6121)
likelihood.normal = function(par, data){
  mu = par[1]
  sig = par[2]
  joint = dnorm(data, mean = mu, sd = sig)
  return(-sum(log(joint)))}

opt = optim(c(3,0.1), likelihood.normal, data = x)

mu.hat.mle = opt$par[1]
sig.hat.mle = opt$par[2]
```

```{r}
mu.hat.mle
sig.hat.mle
```

>#### $\hat{\mu}_{MLE} = 3.057459$  , $\hat{\sigma}_{MLE} =  0.4344073$

## (b) According to the question ”if the mean of sepal width is 3”, what is the estimate for the quantity of interest?

>#### We can use $\hat{\mu}_{MLE}$ to estimate $\mu$ , which is the mean of sepal width.

## (c) Construct the 95% confidence interval for the true quantity of interest by bootstrapping.

```{r}
set.seed(6121)
iter = 1000
np.mu.hat = rep(NA,iter)
np.sig.hat = rep(NA,iter)

for (j in 1:iter){
  dataY = sample(x, length(x), replace = TRUE)
  estY = optim(c(3,0.2), likelihood.normal, data = dataY)
  np.mu.hat[j] = estY$par[1]
  np.sig.hat[j] = estY$par[2]
}
```

```{r}
quantile(np.mu.hat, c(0.025, 0.975))
quantile(np.sig.hat, c(0.025, 0.975))
```

>#### The 95% C.I. for the true quantity of interest by bootstrapping is [2.992, 3.127]

## (d) Based on the 95% confidence interval in (c), how would you conclude the question ”if the mean of sepal width is 3”?

>#### We can say that "the mean of sepal width is 3" because 3 is in the interval [2.992, 3.127].

## (e) If I use a one-sample t-test to test if $H_{0} : \mu = 3$, is the conclusion as the same as the result in (d)?

```{r}
t.test(x, alternative = 'two.sided', mu = 3)
```

>#### The P-value > 0.05, so we do not reject the $H_{0}$. Therefore, we don't have sufficient evidance to claim that "the mean of sepal width is not 3", so the conclusion is as the same as the result in (d).
